Search for Spatially Extended Fermi-LAT Sources Using Two Years of Flight Data

### 2011-08-16 extended_catalog/paper/extended_catalog.tex
lots of keiths changes

Based on size vs. physical distance considerations,
we expect most extended sources to be inside our Galaxy.  Unfortunately, the \gev emission
in the Galactic plane is dominated by extremely structured 
diffuse emission from the interactions of cosmic rays with the
intergalactic medium.  Finding sources on top of this emission is difficult
\citep{first_diffuse_paper} as has been discussed in 1FGL and 2FGL
\citep{first_cat,second_cat}.  Furthermore, the Galactic plane is crowded
and it is often difficult to correctly model nearby sources.  Because of this,
finding a source with $\tsext>16$ is not a sufficient
criteria for resolving a source. For each extended source,
we perform several analysis crosschecks.

For each candidate, we generated a map of residual \ts by adding a new
source of spectral index 2 into the region and finding the increase in
likelihood when fitting its flux. \ts maps are useful to look for residual
structure in the sky mode.  Figure~\ref{res_tsmaps} shows a residual \ts
map for the extended source IC443.  We also generated plots of the sum of
all counts within a given distance of the source and compared it to the
model predictions of a point source.  The plots were binned uniformly
in $\Delta \theta^2$ so that an isotropic background would be flat.
An example radial integral plot is shown for the extended source IC443
in figure~\ref{four_plots_ic443}(c).  For each source, we also made
Galactic and extragalactic diffuse emission subtracted smoothed counts
maps. Figure~\ref{four_plots_ic443}(d) shows an example for IC443.

>>>>

Based on size vs. physical distance considerations,
we expect most extended sources to be located inside our Galaxy
adn thus to be concentrated along the Galactic plane.  Unfortunately, the \gev emission
in the Galactic plane is dominated by extremely structured 
diffuse emission from the interactions of cosmic rays with the
interstellar medium.  Finding sources on top of this emission is difficult
\citep{first_diffuse_paper} as has been discussed in 1FGL and 2FGL
\citep{first_cat,second_cat}.  Furthermore, the Galactic plane is crowded
and it is often difficult to correctly model nearby sources.  Because of this,
finding a source with $\tsext>16$ is not a sufficient
criteria for resolving a source. For each extended source,
we perform several analysis crosschecks.

For each candidate, we generated a map of residual \ts by adding a new
source of spectral index 2 into the region and finding the increase in
likelihood when fitting its flux. \ts maps are useful to look for residual
structure in the sky model.  Figure~\ref{res_tsmaps} shows a residual \ts
map for the extended source IC443.  The residual \ts map indicates that
the spatially extended model for IC443 is a significantly better description
of the observed photons.
We also generated plots of the sum of
all counts within a given distance of the source and compared it to the
model predictions of a point source.  
An example radial integral plot is shown for the extended source IC443
in figure~\ref{four_plots_ic443}(c).  For each source, we also made
Galactic and extragalactic diffuse emission subtracted smoothed counts
maps. Figure~\ref{four_plots_ic443}(d) shows an example for IC443.
